%-------------------------
% Resume in LateX
% Author : Brandon High
% Based on work by : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Custom Bullets
\renewcommand{\labelitemi}{\textsc{}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
\item[\textsc{}]\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://bmh.io/}{\Large Brandon High}} & Email: \href{mailto:hire@bmh.io}{hire@bmh.io}\\
  \href{https://bmh.io/}{bmh.io} & Linkedin: \href{https://www.linkedin.com/in/brandonhighthesoftwareguy/}{brandonhighthesoftwareguy}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Corvallis, OR}
      {Bachelors of Science in Computer Science, Minor Psychology}{Fall 2005 -- Spring 2010}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {Ride with GPS}{Portland, OR}
  {Staff Modern Linux Systems and Software Engineer}{Feb 2024 -- Apr 2025}
  \resumeItemListStart
    \resumeItem{Argo Workflows}
      {Led adoption for CI/CD and data pipelines; integrated with Rails tooling.}
    \resumeItem{Kubernetes Administration}
      {Managed staging deployments and planned legacy production migration.}
    \resumeItem{Observability}
      {Maintained stack: Grafana, Prometheus, Elasticsearch, Kibana, Sensu, Munin.}
    \resumeItem{Automation}
      {Used Ansible and Python to manage bare metal hardware configuration.}
    \resumeItem{Data Center Ops}
      {Upgraded frontend systems and network hardware for redundancy. Maintained existing Ubuntu Linux systems.}
    \resumeItem{On-Call}
      {Participated in PagerDuty rotation for incident response.}
  \resumeItemListEnd

\resumeSubheading
  {OpenGov}{Remote}
  {Staff \& Senior Software Engineer (Delivery Engineering)}{Jul 2020 -- Jan 2024}
  \resumeItemListStart
    \resumeItem{CI/CD Modernization}
      {Migrated from Jenkins/Spinnaker to GitHub Actions and ArgoCD; built open-source Actions in Python, TypeScript, and Bash. Ran self-hosted GitHub Actions runners on Kubernetes.}
    \resumeItem{AI \& Internal Tools}
      {Prototyped PR Review Bot using TypeScript/LangChain; managed OpenAI Org access.}
    \resumeItem{Access Control}
      {Architected and implemented org-wide RBAC via Terraform/Teleport for AWS and Kubernetes.}
    \resumeItem{Infrastructure as Code}
      {Built and tested Terraform modules with Terratest (golang). Built and maintained Org AWS AMIs with Packer.}
    \resumeItem{Observability \& Monitoring}
      {Collaborated on internal Grafana "Observability as Code" platform that provided metrics/logs/traces/SLOs/alerts for teams automatically using Terraform triggered via Git. Managed underlying Grafana Cloud, in-cluster agents/Prometheus.}
    \resumeItem{SRE \& Dev Enablement}
      {Led Kubernetes, Helm, Docker, AWS, secrets management, security and observability efforts; supported on-call via OpsGenie.}
    \resumeItem{Open Source}
      {Attended Kubecon 2023. Contributions to Argo projects, CNCF, Kubernetes, Kustomize.}
  \resumeItemListEnd

\resumeSubheading
  {Puppet}{Portland, OR}
  {Senior Software Engineer (Dev Infrastructure Ops)}{Aug 2018 -- Jul 2020}
  \resumeItemListStart
    \resumeItem{Observability}
      {Unified logging (FluentD) and tracing with OpenTracing/OpenTelemetry/Jaeger.}
    \resumeItem{Cloud Migration}
      {Migrated Jenkins and Ruby services to GKE; supported vSphere, Mesos, Docker.}
    \resumeItem{Team Leadership}
      {Served as Scrum Master and Product Owner; drove backlog alignment and cross-team communication.}
  \resumeItemListEnd

\resumeSubheading
  {Puppet (formerly Puppet Labs)}{Portland, OR}
  {Software Engineer (Puppet Enterprise Installer/Integration Team)}{Dec 2013 -- Aug 2018}
  \resumeItemListStart
    \resumeItem{Installer \& Orchestrator}
      {Co-architected and implemented GUI Installer and Orchestrator using Ruby/Sinatra. This automated the install, upgrade, and configuration of our enterprise multi-service distributed system in airgapped customer environments. Responsible for integration testing of all Puppet components into this distribution.}
    \resumeItem{Open Source Contributions}
      {Created Chloride SSH library, ruby-pathspec, and rubocop-i18n.}
    \resumeItem{CI Tooling}
      {Developed internal Jenkins tools and shared Groovy libraries.}
  \resumeItemListEnd

\resumeSubheading
  {Facebook Inc.}{Menlo Park, CA}
  {Site Reliability Engineer}{May 2012 -- Nov 2013}
  \resumeItemListStart
    \resumeItem{Tooling}
      {Built Python tools for incident remediation and infrastructure audit.}
    \resumeItem{Platform Migration}
      {Supported shift to in-house containerization (CGroups-based, Borg-like).}
    \resumeItem{On-Call}
      {Handled production incidents as part of SRE rotation.}
  \resumeItemListEnd

\resumeSubheading
  {Flashlight LLC}{Portland, OR}
  {Software Engineer}{Sep 2010 -- Apr 2012}
  \resumeItemListStart
    \resumeItem{UI Development}
      {Built Groovy/Grails/jQuery frontend for cable STB control.}
    \resumeItem{Automation}
      {Automated dev environment setup with Puppet.}
  \resumeItemListEnd


% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications and Post-Academic Education}
  \resumeSubHeadingListStart
    \resumeSubItem{Kubernetes Certified Application Developer}
      {Linux Foundation – 2021}
    \resumeSubItem{Machine Learning Nanodegree}
      {Udacity – Jan 2017 to Jul 2017; coursework included Linear Regression, Neural Networks, and TensorFlow}
    \resumeSubItem{Docker Certified Associate}
      {Docker – Jun 2018 to Jun 2020 (Expired)}
    \resumeSubItem{Puppet Professional Certification}
      {Puppet – May 2015}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/kustomize-everything/}{kustomize-everything}}
      {Suite of GitHub actions for working with Kustomize/GitOps using the Rendered YAML Manifests GitOps pattern.}
    \resumeSubItem{\href{https://github.com/highb/asdf-teleport-ent}{asdf-teleport-ent}}
      {asdf plugin for managing Teleport CLI versions.}
    \resumeSubItem{\href{https://github.com/highb/bad-parrots}{bad-parrots}}
      {Collection of scripts for working with local LLMs in Docker.}
    \resumeSubItem{\href{https://github.com/highb/pathspec-ruby}{pathspec-ruby}}
      {Ruby library for parsing .gitignore-like files.}
    \resumeSubItem{\href{https://github.com/highb/resume}{resume}}
      {\LaTeX source for this document.}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Python, Ruby, JavaScript/TypeScript, Bash, C, C++, Go/golang, Rust, SQL, Elixir, Clojure, x86 ASM, Zig, Nim, AWK, Haskell, Lua, PHP, Prolog, Lisp}
    \resumeSubItem{CI/CD}
      {GitHub Actions, Argo Workflows, ArgoCD, Argo Events, CircleCI, Jenkins, Spinnaker}
    \resumeSubItem{Infrastructure \& Automation}
      {Terraform, Kubernetes, Helm, Kustomize, Ansible, Puppet, Docker}
    \resumeSubItem{Cloud}
      {AWS, GCP}
    \resumeSubItem{Observability \& Monitoring}
      {Prometheus, Grafana, Elasticsearch, Kibana, FluentD, OpenTracing, OpenTelemetry, Sensu, Munin}
    \resumeSubItem{Security \& Access Control}
      {RBAC, Teleport, IAM (AWS)}
    \resumeSubItem{AI/LLM}
      {OpenAI API, OLlama, LangChain}
    \resumeSubItem{Testing \& Dev Tools}
      {Terratest (Golang), Git, VSCode, Vim, Groovy (Jenkins Pipelines)}
    \resumeSubItem{Operating Systems}
      {Linux (Ubuntu/Debian/CentOS/Arch Linux/Gentoo/Raspbian), macOS, Windows}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
